Introduction to VEScenarios

### 2021-04-20 sources/models/VEScenarios/tutorial_VEScenario.Rmd
Run the Rmarkdown without evaluation
- User will need to step through the code themselves to modify the scenarios before BuildScenarios step

---
title: "Introduction to VERRSPM_Scenario"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to VETRSPM_Scenario}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, setup, include=FALSE}
# When running RMarkdown file, the working directory is the location of the file itself.
# We want to run this from the root of the VisionEval installation. It may be 've.runtime' when testing a developer-built version, or ve.root # when using an end user installed version.
use_dir = ifelse(grepl(ve.runtime, getwd()), ve.runtime, ve.root)

@@

Strategic planning often requires the assessment of large numbers of future scenarios, each assessing a different combination of prioritizations, policy decisions, and constraints. The VEScenarios module provides the capability to quickly set up, run, and visualize large numbers of VERSPM scenarios using a baseline scenario combined with multiple changes to model inputs.

@@

### Scenario manager database
The first step to run VEScenario is to build the scenario manager database. 
The database should be a csv file in standard format defined and has the following attributes:

strategy_label: A concise headline label for a Strategy used in downstream visualizations, e.g., Community Design.
strategy_description: A verbose description of the Strategy explaining its meaning, e.g., “Local policies to enable shorter trips and travel by alternate modes.” 
strategy_level: An integer index unique to each strategy level, e.g., “1”. 
category_name: A single unique letter used to define the relevant Category and used to name scenario folders, e.g., “L”. 
category_label: A concise headline label for the Category used in downstream visualizations, e.g., “Land Use”. 
category_description: A verbose description of the Category explaining its meaning, e.g., “Distribution of population and employment by place type”. 
category_instructions: Additional meta-data describing the specific way in which the relevant model will impact this category, e.g., “The form in which development occurs (density, regional accessibility, mixed use, etc.) represented by the distribution of population and employment by place type”. 
policy_name: A single number used to define the relevant Policy and used to name scenario folders, e.g., “1”
policy_label: A concise headline label for the Policy used in downstream visualizations, e.g., “Base”. The keywords Base or Baseline indicated that the files from the Scenario Baseline Input Folder (see below) are not expected to be edited.  
policy_description: A verbose description of the Policy explaining its meaning, e.g., “Maintain current distribution”. 
input_label: A numeric index uniquely identifying an input file needed to implement the Policy within the model. 
input_filename: The name of the file that implements the policy.

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
ScenarioManagerFile = "models/VEScenarios/scenario_inputs/verspm_scenario_manager.csv"
ModelFolder = "models/VERSPM"
VEScenario::NewScenarioSetInterior(ScenarioManagerFile,
                                  ModelFolder,
                                  ScenarioInputFolder = NULL,
                                  ScenarioBaselineInputFolder = NULL)
```

@@

** ScenarioInputFolder — a file path identifying the location on the computer hard disk where the inputs for the scenarios will be located. In case ScenarioManagerFile is in this folder, it can be NULL.
** ScenarioManagerFile — the file path of the CSV file described above, which is expected ( but not required) to be in the ScenarioInputFolder. 
** ModelFolder — The path to the folder containing the Base Model run_model.R  script that will run each of the constructed scenarios plus its other elements (inputs and defs sub-folders).
** ScenarioBaselineInputFolder — the location on the computer of the hard disk where the inputs used for the baseline scenarios are located. In case the folder it inside the ModelFolder it can be NULL

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
ScenarioInputFolder = "models/VEScenarios/scenario_inputs"
ScenarioOutputFolder ="models/VEScenarios/scenarios"

@@

** ScenarioInputFolder — described above
** ModelFolder — Described above
** ScenarioOutputFolder — file path identifying the location on the computer hard disk where the built scenarios will be located

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
ve.run()
VEScnearios_test <- openModel("VEScenarios")
VEScnearios_test$run()
```

>>>>

---
title: "Introduction to VEScenarios"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to VEScenarios}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, setup1, include=FALSE, eval=T}
knitr::opts_chunk$set(echo=TRUE, eval=FALSE)
```

```{r, setup2, include=FALSE}
# When running RMarkdown file, the working directory is the location of the file itself.
# We want to run this from the root of the VisionEval installation. It may be 've.runtime' when testing a developer-built version, or ve.root # when using an end user installed version.
use_dir = ifelse(grepl(ve.runtime, getwd()), ve.runtime, ve.root)

@@

Strategic planning often requires the assessment of large numbers of future scenarios, each assessing a different combination of prioritizations, policy decisions, and constraints. The VEScenario module provides the capability to quickly set up, run, and visualize large numbers of VisionEval scenarios using a baseline scenario combined with multiple changes to model inputs.

@@

### Scenario manager database

The first step to run VEScenarios is to build the scenario manager database. 
The database should be a csv file in standard format defined and has the following attributes:

- strategy_label: A concise headline label for a Strategy used in downstream visualizations, e.g., Community Design.
- strategy_description: A verbose description of the Strategy explaining its meaning, e.g., “Local policies to enable shorter trips and travel by alternate modes.” 
- strategy_level: An integer index unique to each strategy level, e.g., “1”. 
- category_name: A single unique letter used to define the relevant Category and used to name scenario folders, e.g., “L”. 
- category_label: A concise headline label for the Category used in downstream visualizations, e.g., “Land Use”. 
- category_description: A verbose description of the Category explaining its meaning, e.g., “Distribution of population and employment by place type”. 
category_instructions: Additional meta-data describing the specific way in which the relevant model will impact this category, e.g., “The form in which development occurs (density, regional accessibility, mixed use, etc.) represented by the distribution of population and employment by place type”. 
- policy_name: A single number used to define the relevant Policy and used to name scenario folders, e.g., “1”
policy_label: A concise headline label for the Policy used in downstream visualizations, e.g., “Base”. The keywords Base or Baseline indicated that the files from the Scenario Baseline Input Folder (see below) are not expected to be edited.  
- policy_description: A verbose description of the Policy explaining its meaning, e.g., “Maintain current distribution”. 
- input_label: A numeric index uniquely identifying an input file needed to implement the Policy within the model. 
- input_filename: The name of the file that implements the policy.

@@

```{r new_scenario_set}
ScenarioManagerFile = "models/VEScenarios/scenario_inputs/verspm_scenario_manager.csv"
ModelFolder = "models/VERSPM"
VEScenario::NewScenarioSetInterior(ScenarioManagerFile,
                                  ModelFolder,
                                  ScenarioInputFolder = NULL,
                                  ScenarioBaselineInputFolder = NULL)
```

@@

- **ScenarioInputFolder** — a file path identifying the location on the computer hard disk where the inputs for the scenarios will be located. In case ScenarioManagerFile is in this folder, it can be NULL.
- **ScenarioManagerFile** — the file path of the CSV file described above, which is expected ( but not required) to be in the ScenarioInputFolder. 
- **ModelFolder** — The path to the folder containing the Base Model run_model.R  script that will run each of the constructed scenarios plus its other elements (inputs and defs sub-folders).
- **ScenarioBaselineInputFolder** — the location on the computer of the hard disk where the inputs used for the baseline scenarios are located. In case the folder it inside the ModelFolder it can be NULL

@@

```{r build_scenarios}
ScenarioInputFolder = "models/VEScenarios/scenario_inputs"
ScenarioOutputFolder = "models/VEScenarios/scenarios"

@@

- **ScenarioInputFolder** — described above
- **ModelFolder** — Described above
- **ScenarioOutputFolder** — file path identifying the location on the computer hard disk where the built scenarios will be located

@@

```{r run_scenarios}
ve.run()
VEScnearios_test <- openModel("VEScenarios")
VEScnearios_test$run()
```
